### 2015-06-17 src/5_3_Proposal.tex
reparando algo
pequeños detalles
Gráficos experimentos VECM vs OPT
plot de datos y distribución

\section{\uppercase{Methodology}}
\label{sec:methodology}

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
$\mathbf{y}$: matrix with $N$ input vectors and $l$ time series\\
$p$: number of past values \\
method: \{'OLS','RR','AAR'\} \\
$\lambda$: regularization parameter (only requires for RR and AAR methods) \\
$L$: window size of data($L<N$) \\
$\text{mean\_error}$: MAPE threshold \\
$n$: windows size to obtain in-sample MAPE \\
\ENSURE  $\,$ \\
$\{\mathbf{y}_{\text{pred}}[L+1],\dots, \mathbf{y}_{\text{pred}}[N]\}$: model predictions 
\STATE solver = new \texttt{Solver}(method,$\lambda$) \\
\FOR { $t =1$ to $N-L$ }
    \STATE $\mathbf{Y} \gets \mathbf{y}[t:t+L-1]$
    \STATE $\mathbf{y}_t \gets \mathbf{y}[t+L]$
	\IF {$t = 1$}
	    \STATE{$v \gets \texttt{getJohansen}(\mathbf{Y},p)$}
	    \STATE{$[\mathbf{A} \quad \mathbf{B}] \gets
        \texttt{vecMatrix}(\mathbf{Y},p,v)$}
        \STATE \texttt{solver.init\_model($\mathbf{A},\mathbf{B}$)} 
    \ENDIF
	\STATE{$[\mathbf{a}_t \quad \mathbf{b}_t] \gets
    \texttt{vecMatrixOnline}(\mathbf{Y},\mathbf{y}_t,p,v)$}
    \STATE $[\mathbf{X} \quad \mathbf{y}_{\text{pred}}[t]] \gets \texttt{solver.regression}
    (\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}_t)$
    \STATE $\mathbf{Y}_{\text{pred}} = \mathbf{AX}[-n:]+\mathbf{Y}[-n-1:-1]$
    \STATE $\mathbf{e} = \texttt{mape}(\mathbf{Y}_{\text{pred}},\mathbf{Y}[-n:])$
    \IF {$\texttt{mean}(\mathbf{e}) > \text{mean\_error}$}
	    \STATE{$v \gets \texttt{getJohansen}(\mathbf{Y},p)$}
	    \STATE{$\mathbf{A} \gets
        \texttt{vecMatrixUpdate}(\mathbf{A},\mathbf{Y},p,v)$}
        \STATE \texttt{solver.init\_model($\mathbf{A},\mathbf{B}$)} 
	    \STATE{$[\mathbf{a}_t \quad \mathbf{b}_t] \gets
        \texttt{vecMatrixOnline}(\mathbf{Y},\mathbf{y}_t,p,v)$}
        \STATE $[\mathbf{X} \quad \mathbf{y}_{\text{pred}}[t]] \gets \texttt{solver.regression}
        (\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}_t)$
    \ENDIF
\STATE{$[\mathbf{A} \quad \mathbf{B}] \gets
\texttt{matrixUpdate}(\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}t)$}
\ENDFOR
\end{algorithmic}
\caption{OVECM: Online VECM}
\label{alg:proposal}
\end{algorithm}

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
method: \{'OLS','RR','AAR'\} \\
$\mathbf{A}$: VECM design matrix \\
$\mathbf{B}$: VECM dependant variables \\
$\mathbf{a}_t$: new row of $\mathbf{A}$ \\
$\mathbf{b}_t$: new row of $\mathbf{B}$ \\
$\gamma$: regularization parameter \\
$n$: windows size to obtain in-sample MAPE \\
\ENSURE  $\,$ \\
$\mathbf{X}$: regression solution \\
$\mathbf{e}$: in-sample MAPE \\
%\quad \\
%\texttt{init}($L,\lambda$)
%\STATE self.L = L
%\STATE self.lambda = $\lambda$
\quad \\
\texttt{init\_model}($\mathbf{A},\mathbf{B}$)\\
\IF {method == 'RR' or method == 'AAR'}
\STATE $ [m \quad n] = \text{size}(\mathbf{A}) $ 
\STATE $\mathbf{S} = \displaystyle \sum_{i=1}^m \mathbf{a}_i \mathbf{a}_i^\top + \gamma \mathbb{I}$
\STATE $\mathbf{W} = \displaystyle \sum_{i=1}^m \mathbf{a}_i \mathbf{b}_i$
\ENDIF \\
\quad \\
\texttt{regression}($\mathbf{A},\mathbf{B},\mathbf{a_t},\mathbf{b_t},n$) \\
\IF {method == 'OLS'}
        \STATE $\mathbf{X}=(\mathbf{A}^\top \mathbf{A})^{-1}\mathbf{A}^\top
        \mathbf{B}$
\ELSIF {method == 'RR'}
        \STATE $\mathbf{X} = \mathbf{S}^{-1} \mathbf{W} $
        \STATE $\mathbf{S} = \mathbf{S}+
        \mathbf{a}_t \mathbf{a}_t^\top-
        \mathbf{a}_1 \mathbf{a}_1^\top$
        \STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{b}_t$
\ELSIF {method == 'ARR'}
        \STATE $\mathbf{S} = \mathbf{S}+
        \mathbf{a}_t \mathbf{a}_t^\top-
        \mathbf{a}_1 \mathbf{a}_1^\top$
        \STATE $\mathbf{X} = \mathbf{S}^{-1} \mathbf{W} $
        \STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{b}_t$
\ENDIF
\STATE $\mathbf{y}_{\text{pred}} = \mathbf{X}^\top \mathbf{a}_t$
\end{algorithmic}
\caption{Solver Class for Regression Methods}
\label{alg:solver}
\end{algorithm}

@@

>>>>

\section{Methodology}

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
$\mathbf{y}$: matrix with $N$ input vectors and $l$ time series\\
$p$: number of past values \\
method: \{'OLS','RR','AAR'\} \\
$\lambda$: regularization parameter (only requires for RR and AAR methods) \\
$L$: window size of data($L<N$) \\
$\text{mean\_error}$: MAPE threshold \\
$n$: windows size to obtain in-sample MAPE \\
\ENSURE  $\,$ \\
$\{\mathbf{y}_{\text{pred}}[L+1],\dots, \mathbf{y}_{\text{pred}}[N]\}$: model predictions 
\STATE solver = new \texttt{Solver}(method,$\lambda$) \\
\FOR { $t =1$ to $N-L$ }
    \STATE $\mathbf{Y} \gets \mathbf{y}[t:t+L-1]$
    \STATE $\mathbf{y}_t \gets \mathbf{y}[t+L]$
	\IF {$t = 1$}
	    \STATE{$v \gets \texttt{getJohansen}(\mathbf{Y},p)$}
	    \STATE{$[\mathbf{A} \quad \mathbf{B}] \gets
        \texttt{vecMatrix}(\mathbf{Y},p,v)$}
        \STATE \texttt{solver.init\_model($\mathbf{A},\mathbf{B}$)} 
    \ENDIF
	\STATE{[$\mathbf{A} \quad \mathbf{B} \quad \mathbf{a}_t \quad \mathbf{a}_L \quad \mathbf{b}_t \quad
    \mathbf{b}_L ] \gets
    \texttt{vecMatrixOnline}(\mathbf{Y},\mathbf{y}_t,p,v)$}
    \STATE $[\mathbf{X} \quad \mathbf{y}_{\text{pred}}[t]] \gets \texttt{solver.regression}
    (\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}_t)$
    \STATE $\mathbf{Y}_{\text{pred}} = \mathbf{AX}[-n:]+\mathbf{Y}[-n-1:-1]$
    \STATE $\mathbf{e} = \texttt{mape}(\mathbf{Y}_{\text{pred}},\mathbf{Y}[-n:])$
    \IF {$\texttt{mean}(\mathbf{e}) > \text{mean\_error}$}
	    \STATE{$v \gets \texttt{getJohansen}(\mathbf{Y},p)$}
	    \STATE{$\mathbf{A} \gets
        \texttt{vecMatrixUpdate}(\mathbf{A},\mathbf{Y},p,v)$}
        \STATE \texttt{solver.init\_model($\mathbf{A},\mathbf{B}$)} 
	    \STATE{$[\mathbf{a}_t \quad \mathbf{b}_t] \gets
        \texttt{vecMatrixOnline}(\mathbf{Y},\mathbf{y}_t,p,v)$}
        \STATE $[\mathbf{X} \quad \mathbf{y}_{\text{pred}}[t]] \gets \texttt{solver.regression}
        (\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}_t)$
    \ENDIF
\STATE{$[\mathbf{A} \quad \mathbf{B}] \gets
\texttt{matrixUpdate}(\mathbf{A},\mathbf{B},\mathbf{a}_t,\mathbf{b}t)$}
\ENDFOR
\end{algorithmic}
\caption{OVECM: Online VECM}
\label{alg:proposal}
\end{algorithm}

@@

\begin{algorithm}[ht]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
method: \{'OLS','RR','AAR'\} \\
$\mathbf{A}$: VECM design matrix \\
$\mathbf{B}$: VECM dependant variables \\
$\mathbf{a}_t$: new row of $\mathbf{A}$ \\
$\mathbf{b}_t$: new row of $\mathbf{B}$ \\
$\gamma$: regularization parameter \\
$n$: windows size to obtain in-sample MAPE \\
\ENSURE  $\,$ \\
$\mathbf{X}$: regression solution \\
$\mathbf{e}$: in-sample MAPE \\
%\quad \\
%\texttt{init}($L,\lambda$)
%\STATE self.L = L
%\STATE self.lambda = $\lambda$
\quad \\
\texttt{init\_model}($\mathbf{A},\mathbf{B}$)
\STATE $ [m \quad n] = \text{size}(\mathbf{A}) $ 
\STATE $\mathbf{S} = \displaystyle \sum_{i=1}^m \mathbf{a}_i \mathbf{a}_i^\top + \gamma \mathbb{I}$
\STATE $\mathbf{W} = \displaystyle \sum_{i=1}^m \mathbf{a}_i \mathbf{b}_i$
\quad \\
\texttt{regression}($\mathbf{A},\mathbf{B},\mathbf{a_t},\mathbf{b_t}$) \\
\IF {method == 'OLS'}
        \STATE $\mathbf{X}=(\mathbf{A}^\top \mathbf{A})^{-1}\mathbf{A}^\top
        \mathbf{B}$
\ELSIF {method == 'RR'}
        \STATE $\mathbf{X} = \mathbf{S}^{-1} \mathbf{W} $
        \STATE $\mathbf{S} = \mathbf{S}+
        \mathbf{a}_t \mathbf{a}_t^\top-
        \mathbf{a}_1 \mathbf{a}_1^\top$
        \STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{b}_t$
\ELSIF {method == 'ARR'}
        \STATE $\mathbf{S} = \mathbf{S}+
        \mathbf{a}_t \mathbf{a}_t^\top-
        \mathbf{a}_1 \mathbf{a}_1^\top$
        \STATE $\mathbf{X} = \mathbf{S}^{-1} \mathbf{W} $
        \STATE $\mathbf{W} = \mathbf{W} + \mathbf{a}_t \mathbf{b}_t$
\ENDIF
\STATE $\mathbf{y}_{\text{pred}} = \mathbf{X}^\top \mathbf{a}_t$
\end{algorithmic}
\caption{Solver Class for Regression Methods}
\label{alg:solver}
\end{algorithm}

@@

\section{Experiments}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/forexdata}
  \caption{10 seconds frequency forex data for EURUSD, GBPUSD and USDJPY}
  \label{fig:forexdata}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/distdata}
  \caption{Distribution of EURUSD, GBPUSD and USDJPY data}
  \label{fig:distdata}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.9\textwidth]{img/onlinecomparison}
  \caption{Cumulative loss of AAR, RR and OLS solutions for VECM against its optimal algorithm}
  \label{fig:onlinecomparison}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.9\textwidth]{img/RRcomparison}
  \caption{Cumulative loss RR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:RRcomparison}
\end{figure}

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.9\textwidth]{img/AARcomparison}
  \caption{Cumulative loss AAR VECM against its optimal algorithm using different $\lambda$ values}
  \label{fig:AARcomparison}
\end{figure}
